MCC Novelty Kids

### 2018-07-27 stats/mcc_inf.kids.Rmd
updating kids novelty

There was a small tendency in the adult data to pick the inner object in the control condition (55% of cases). This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field. For the 3yo, it seems like the tendency to pick the object closer to the agent is much stronger and is in fact driving their choice. The plot below shows the proportion of trials in which they picked the inner object. If position would not matter, this should be at chance in each condition.

>>>>

There was a small tendency in the adult data to pick the inner object in the control condition (55% of cases). This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field (see below).

![Setup as is.](../../../setup_inf.png)

For the 3yo, it seems like the tendency to pick the object closer to the agent is much stronger and is in fact driving their choice. The plot below shows the proportion of trials in which they picked the inner object. If position would not matter, this should be at chance in each condition.

### 2018-07-27 stats/mcc_novel.kids.Rmd
updating kids novelty

---
title: "MCC Preference Kids"
author: "Manuel Bohn"
date: "23 7 2018"
output: html_document
---

@@

d_ipad <- read_csv(file="kids_pref.data.csv")

d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
  mutate(age_num = as.numeric(as.character(age_num)))

d <- bind_rows(d_ipad,d_hand_code)%>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
  filter(subid != "200718_8_pref")

@@

There was one additional 4yo in the data set, whom I excluded to get the pre-registered sample size of 45 total. For the modeling we might want to include her as that gives us a tiny bit more precision.

@@

All training trials were answered correctly, suggesting that children generally understood the procedure. Sex is not included in the data set but the sex ration is fairly balances across age bins (47 to 60% girls).

@@

Just to check if we got the planned sample size of 15 per bin.

@@

Medium overall effect of speaker change.

@@

With age as continuous variable. We pre-registered the model with an interaction between age and change as a random slope for subject: `(change * age| subid)`. However, including age here seems unnecessary since each subject has only one age. I therefore took the interaction out in the model below.

Results mirror what we see in the plots above: increasing effect of speaker change across development.

>>>>

---
title: "MCC Novelty Kids"
author: "Manuel Bohn"
date: "23 7 2018"
output: html_document
---

@@

d<- read_csv(file="kids_novel.data.csv")%>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

@@

@@

@@

@@
